Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-20 manuscript.tex
Add more detailed figures for the geo transfer

\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.5\textwidth]{third_reachability_set} % requires the graphicx package
   \caption{Reachable set after three iterations}
   \label{fig:third_reachability_set}
\end{figure}
Next, we generate the stable invariant manifold associated with the periodic orbit in order to determine our target set.
The stable manifold is propagated to the \Poincare section at \( y = 0 \), which is denoted by the horizontal black line in~\cref{fig:geo_transfer_full}.
Next, we compute the reachable sets originating on the geo-stationary orbit and subject to the maximum control constraint. 
The multiple shooting approach is used to solve the optimal control problem with two segments.
For the first reachability set computation, the initial geostationary orbit is used to initialize the multiple shooting algorithm.
We use the same initial guess of \( \vecbf{\lambda}_0\) as in~\cref{sec:periodic_orbit_transfer} and propogate over the fixed time horizon of the period of the geostationary orbit to initialize \( \vecbf{\lambda}_i^{-}\).

>>>>

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage1_trajectory_zoom.pdf} 
        \caption{Stage 1 Trajectory~\label{fig:stage1_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage1_poincare.pdf} 
        \caption{Stage 1 \Poincare~section \label{fig:stage1_poincare}} 
    \end{subfigure}

    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage2_trajectory_zoom.pdf} 
        \caption{Stage 2 Trajectory~\label{fig:stage2_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage2_poincare.pdf} 
        \caption{Stage 2 \Poincare~section \label{fig:stage2_poincare}} 
    \end{subfigure}

    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage3_trajectory_zoom.pdf} 
        \caption{Stage 3 Trajectory~\label{fig:stage3_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage3_poincare.pdf} 
        \caption{Stage 3 \Poincare~section \label{fig:stage3_poincare}} 
    \end{subfigure}

    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage5_trajectory_zoom.pdf} 
        \caption{Stage 4 Trajectory~\label{fig:stage4_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage4_poincare.pdf} 
        \caption{Stage 4 \Poincare~section \label{fig:stage4_poincare}} 
    \end{subfigure}   
    \caption{Stage 1-4 reachability sets: The first four reachability sets visualized in both the position (left) and \Poincare space (right).
        The minimum trajectories from the preceeding stages are shown in red, while the next stage is shown in blue.
    The transfer goal is to generate a complete trajectory from the initial geostationary orbit to the \( L_1 \) stable manifold, with an eventual arrival at the \( L_1 \) periodic orbit~\label{fig:stage1to4_reachability}}
\end{figure}

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage5_trajectory_zoom.pdf} 
        \caption{Stage 5 Trajectory~\label{fig:stage5_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage5_poincare.pdf} 
        \caption{Stage 5 \Poincare~section \label{fig:stage5_poincare}} 
    \end{subfigure}

    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage6_trajectory_zoom.pdf} 
        \caption{Stage 6 Trajectory~\label{fig:stage6_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage6_poincare.pdf} 
        \caption{Stage 6 \Poincare~section \label{fig:stage6_poincare}} 
    \end{subfigure}

    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage7_trajectory_zoom.pdf} 
        \caption{Stage 7 Trajectory~\label{fig:stage7_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage7_poincare.pdf} 
        \caption{Stage 7 \Poincare~section \label{fig:stage7_poincare}} 
    \end{subfigure}

    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage8_trajectory_zoom.pdf} 
        \caption{Stage 8 Trajectory~\label{fig:stage8_trajecotry_zoom}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/geo_transfer/stage8_poincare.pdf} 
        \caption{Stage 8 \Poincare~section \label{fig:stage8_poincare}} 
    \end{subfigure}   
    \caption{Stage 5-8 reachability sets: The last four reachability sets visualized in both the position (left) and \Poincare space (right).
        The minimum trajectories from the preceeding stages are shown in red, while the next stage is shown in blue.
    The transfer goal is to generate a complete trajectory from the initial geostationary orbit to the \( L_1 \) stable manifold, with an eventual arrival at the \( L_1 \) periodic orbit~\label{fig:stage1to4_reachability}}
\end{figure}
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.5\textwidth]{third_reachability_set} % requires the graphicx package
   \caption{Reachable set after three iterations}
   \label{fig:third_reachability_set}
\end{figure}
Next, we generate the stable invariant manifold associated with the periodic orbit in order to determine our target set.
The stable manifold is propagated to the \Poincare section at \( y = 0 \), which is denoted by the horizontal black line in~\cref{fig:geo_transfer_full}.
Next, we compute the reachable sets originating on the geo-stationary orbit and subject to the maximum control constraint. 
The multiple shooting approach is used to solve the optimal control problem with two segments.
For the first reachability set computation, the initial geostationary orbit is used to initialize the multiple shooting algorithm.
We use the same initial guess of \( \vecbf{\lambda}_0\) as in~\cref{sec:periodic_orbit_transfer} and propogate over the fixed time horizon of the period of the geostationary orbit to initialize \( \vecbf{\lambda}_i^{-}\).
